Supplimentary materials

### 2020-10-20 supplimentary_tables.Rmd
post editor comments

# source("r-files/functions.R")
# source("r-files/methods_code.R")
# source("r-files/results_code.R")
load("all_data2.RData")
```

@@

```{r results='asis'}
full <- str %>%
  filter(strength > 0.299 & direction != 0) %>%
  arrange(-strength) %>%
  `colnames<-`(str_replace_all(colnames(.), "_", "\\\\_")) %>%
   mutate_at(c("from", "to"), ~str_replace_all(., "_", "\\\\_")) %>% 
  dendroTools::round_df(2)

@@

```{r results='asis'}
strchange %>%
  filter(strength > 0.299 & direction != 0) %>%
  arrange(-strength) %>%
  `colnames<-`(str_replace_all(colnames(.), "_", "\\\\_")) %>%
   mutate_at(c("from", "to"), ~str_replace_all(., "_", "\\\\_")) %>% 
  dendroTools::round_df(2) %>% 
  kable(
    caption = "",
    longtable = T,
    escape = F,
    format = "latex"
  ) %>% 
  kable_styling(latex_options = ("HOLD_position"))
```

@@

tab3 <- newprobtable(
  tallc,
  c("balance_1", "stiffness_1", "NLE_1", "hours", "clevel"),
  "injured_1",
  "injured",
  avg30
) %>%
  arrange(-prob) %>%
  select(outcome, everything()) %>%
  dendroTools::round_df(2) %>% 
  select(7, 2:6) %>% 
  `colnames<-`(str_replace_all(colnames(.), "_", "\\\\_")) %>% 
  mutate_all(~str_replace_all(., "_", "\\\\_"))

kable(
  tab3,
  caption = "",
    escape = F
) %>%
  kable_styling(latex_options = "HOLD_position")
```

@@

tab4 <- newprobtable(
  tallc,
  c("balance_2", "stiffness_2", "NLE_2", "FFFS_1", "HRV_2"),
  "injured_2",
  "injured",
  avg30
) %>%
  arrange(-prob) %>%
  select(outcome, everything()) %>%
  dendroTools::round_df(2) %>%
  select(7, 2:6) %>%
  `colnames<-`(str_replace_all(colnames(.), "_", "\\\\_"))

  kable(
    tab4,
    caption = "",
    escape = F
  ) %>%
  kable_styling(latex_options = "HOLD_position")

@@

query7 %>%
  mutate_at(vars(nle, stiffness), ~ case_when(
    . == 1 ~ "+1SD",
    . == 0 ~ "mean",
    . == -1 ~ "-1SD"
  )) %>%
  select(prob, hours, pi, nle, stiffness) %>%
  rename(Probability = "prob") %>%
  dendroTools::round_df(2) %>%
  kable(
    .,
    align = "ccccc"
  ) %>%
  kable_styling(latex_options = "HOLD_position") %>%

  row_spec(0,bold=TRUE)
```

>>>>

# source("r-files/functions.R")
# source("r-files/methods_code.R")
# source("r-files/results_code.R")
load("all_data2x.RData")
```

@@

```{r results='asis'}
full <- str %>%
  filter(strength > 0.299 & direction != 0) %>%
  arrange(-strength) %>%
  `colnames<-`(str_replace_all(colnames(.), "_", "\\\\_")) %>%
    mutate(across(1:2, .fns = ~case_when(.x == "pi" ~ "Previous\ninjury",
                                       .x == "gender" ~ "Gender",
                                       .x == "clevel" ~ "Competitive\nlevel",
                                       .x == "hours" ~"Training hours",
                                       .x == "ind_team" ~ "Sport type",
                                       .x == "nlebase" ~ "Baseline\nNLE",
                                       .x == "stiffness_1" ~ "Stiffness_1",
                                       .x == "stiffness_2" ~ "Stiffness_2",
                                       .x == "NLE_1" ~ "Negative life\nevents_1",
                                       .x == "NLE_2" ~ "Negative life\nevents_2",
                                       .x == "RI_1" ~ "Reward\nInterest_1",
                                       .x == "RI_2" ~ "Reward\nInterest_2",
                                       .x == "BIS_1" ~ "Behavioural\nInhibition\nSystem_1",
                                       .x == "BIS_2" ~ "Behavioural\nInhibition\nSystem_2",
                                       .x == "HRV_1" ~ "Heart rate\nvariability_1",
                                       .x == "HRV_2" ~ "Heart rate\nvariability_2",
                                       .x == "balance_1" ~ "Balance_1",
                                       .x == "balance_2" ~ "Balance_2",
                                       .x == "FFFS_1" ~ "Fight-Flight-\nFreeze\nSystem_1",
                                       .x == "FFFS_2" ~ "Fight-Flight-\nFreeze\nSystem_2",
                                       .x == "injured_1" ~ "Injured_1",
                                       .x == "injured_2" ~ "Injured_2"
  ))) %>% 
   mutate_at(c("from", "to"), ~str_replace_all(., "_", "\\\\_")) %>% 
  dendroTools::round_df(2)

@@

```{r results='asis'}
strchange %>%
  filter(strength > 0.299 & direction != 0) %>%
  arrange(-strength) %>% 
  mutate(across(1:2, .fns = ~case_when(.x == "pi" ~ "Previous\ninjury",
                                       .x == "gender" ~ "Gender",
                                       .x == "clevel" ~ "Competitive\nlevel",
                                       .x == "hours" ~"Training\nhours",
                                       .x == "stiffness" ~ "Stiffness",
                                       .x == "nlec" ~ "Negative life\nevents",
                                       .x == "RI" ~ "Reward\ninterest",
                                       .x == "BIS" ~ "Behavioural\nInhibition\nSystem",
                                       .x == "HRV" ~ "Heart rate\nvariability",
                                       .x == "balance" ~ "Balance",
                                       .x == "FFFS" ~ "Fight-Flight-\nFreeze\nSystem",
                                       .x == "injured" ~ "Injured"))) %>%
  `colnames<-`(str_replace_all(colnames(.), "_", "\\\\_")) %>%
   mutate_at(c("from", "to"), ~str_replace_all(., "_", "\\\\_")) %>% 
  dendroTools::round_df(2) %>% 
  kable(
    caption = "",
    longtable = T,
    escape = F,
    format = "latex"
  ) %>% 
  kable_styling(latex_options = ("HOLD_position"))
```

@@

tab3 <- newprobtable(
  tallc,
  c("balance_1", "stiffness_1", "NLE_1", "hours", "clevel"),
  "injured_1",
  "injured",
  avg30
) %>%
  arrange(-prob) %>%
  select(outcome, everything()) %>%
  dendroTools::round_df(2) %>% 
  select(7, 2:6) %>% 
    rename(Probability = "prob",
         "Competitive level" = clevel,
         "Training hours" = hours,
         "Negative life events_1" = "NLE_1") %>% 
  `colnames<-`(str_replace_all(colnames(.), "_", "\\\\_")) %>% 
  mutate_all(~str_replace_all(., "_", "\\\\_"))

kable(
  tab3,
  caption = "",
    escape = F,
  align = "c"
) %>%
  kable_styling(latex_options = "HOLD_position")
```

@@

tab4 <- newprobtable(
  tallc,
  c("balance_2", "stiffness_2", "NLE_2", "FFFS_1", "HRV_2"),
  "injured_2",
  "injured",
  avg30
) %>%
  arrange(-prob) %>%
  select(outcome, everything()) %>%
  dendroTools::round_df(2) %>%
  select(7, 2:6) %>%
    rename(Probability = "prob",
         "Fight-Flight-Freeze System_1" = FFFS_1,
         "Negative life events_2 "= NLE_2,
         "Heart rate variability_2" = "HRV_2",
         Stiffness_2 = stiffness_2,
         Balance_2 = balance_2) %>%
  `colnames<-`(str_replace_all(colnames(.), "_", "\\\\_"))

  kable(
    tab4,
    caption = "",
    escape = F,
    align = "c"
  ) %>%
  kable_styling(latex_options = "HOLD_position") %>% 
      column_spec(c(2,3),width = "2cm") %>% 
  column_spec(5, width = "2.8cm")

@@

query7 %>%
  mutate_at(vars(nle, stiffness), ~ case_when(
    . == 1 ~ "+1SD",
    . == 0 ~ "mean",
    . == -1 ~ "-1SD"
  )) %>%
  select(prob, hours, pi, nle, stiffness) %>%
    rename(Probability = "prob",
         "Training hours" = hours,
         "Previous injury" = pi,
         "Negative life events" = nle,
         Stiffness = stiffness) %>%
  dendroTools::round_df(2) %>%
  kable(
    .,
    align = "ccccc"
  ) %>%
  kable_styling(latex_options = "HOLD_position") %>%
  row_spec(0,bold=TRUE)
```
